Tables with \textbf{xtable} and \textbf{knitr}

### 2016-08-14 src/ArticleReadyTableGenerate.Rnw
getting ready to run pooled LCDM tests, once directory structures are correct

<<Pooled_Stat_Tests>>=
  DATA_DIR = "./data/pooled_analysis/"
  sides =  c("lh","rh")
  regions = c("itg","mtg","stg","antcing","postcing")
  conditions  = c("normal","aMCI","amdMCI","nMCI","nmdMCI")
  comparisons = t(array(c(1,2,1,3,1,4,1,5,2,3,2,4,4,5),dim = c(2,7)))

  pool_stat_tests_all_regions_sides<- list(lh = NULL, rh = NULL)
  for ( side in sides) {
    pool_stat_tests_all_regions_sides[[side]] = list()
    for ( region in regions ) {
      pooled_stats_list = list()

      #read the pooled files 
      for (i in 1:5) {
        cond_fileh <- paste(DATA_DIR,"/",side,'_',region,"_", conditions[i], 
                            "_wave1_pooled_antsy.txt", sep="", collapse ="")
        print (cond_fileh)
        if (! file.exists(cond_fileh)) {
          print (paste0( cond_fileh,
                         " does not exist",sep="",collapse="") )
        }
        pooled_stats <-read.table(file=cond_fileh, nrows = 2.5E6, colClasses = "numeric")
        print (str(pooled_stats_list))
        if ( is.data.frame(pooled_stats_list) ) {
          pooled_stats <- pooled_stats[,1]
        }
        pooled_stats_list <-c(pooled_stats_list,list(pooled_stats))

      }
      pool_stat_tests_all_regions_sides[[side]] <-c(pool_stat_tests_all_regions_sides[[side]], list(pooled_stats_list)) 
      #run the stat tests for the 7 pair comparisons. We may want to limi
      pooled_test_result<-list()
      for ( i in 1:7 ) {
        pooled_test_result <- c(pooled_test_result,list=list())
      }

      p_values<-list(mwu.test=rep(0,7), ks.test = rep(0,7), kolmog.test = rep(0,7))
      for ( i in 1:7 ) {
        cond_1 = comparisons[i,1]
        cond_2 = comparisons[i,2]

        pooled_test_result[[i]] <- ks.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],
                                           alternative="t",exact = NULL)
        p_values$ks.test[i] <-pooled_test_result[[i]]$p.value

        pooled_test_result[[i]] <- wilcox.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],
                                               alternative="t",exact = FALSE,
                                               correct = FALSE)
        p_values$mwu.test[i] <-pooled_test_result[[i]]$p.value
        pooled_test_result[[i]] <- t.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],    
                                           alternative = "t",mu = 0, paired = FALSE, 
                                           var.equal = FALSE, conf.level = 0.95)

        p_values$welcht.test[i] <-pooled_test_result[[i]]$p.value
      }
      pool_stat_tests_all_regions_sides[[side]] <- c(pool_stat_tests_all_regions_sides[[side]],list(pooled_test_result) )
    }
    names(pool_stat_tests_all_regions_sides[[side]]) <- regions
  }

>>>>

<<Pooled_Stat_Tests,cache=TRUE>>=
  DATA_DIR = "./data/pooled_analysis/"
  sides =  c("lh","rh")
  regions = c("itg","mtg","stg","antcing","postcing")
  conditions  = c("normal","aMCI","amdMCI","nMCI","nmdMCI")
  comparisons = t(array(c(1,2,1,3,1,4,1,5,2,3,2,4,4,5),dim = c(2,7)))
  hypothesis_ordinality <- c("two.sided","less","greater")

  pool_stat_tests_all_regions_sides <- matrix(list(), nrow=2,ncol=5,dimnames = list(sides=sides,regions=regions))

  print (str(pool_stat_tests_all_regions_sides))
  pool_stats_all <-  matrix(rep(c(),10), nrow=2,ncol=5,dimnames = list(sides=sides,regions=regions))
  for ( side in sides) {

    for ( region in regions ) {

      pooled_stats_list = list()

      #read the pooled files 
      for (i in 1:5) {
        cond_fileh <- paste(DATA_DIR,"/",side,'_',region,"_", conditions[i], 
                            "_wave1_pooled_antsy.txt", sep="", collapse ="")
        print (cond_fileh)
        if (! file.exists(cond_fileh)) {
          print (paste0( cond_fileh,
                         " does not exist",sep="",collapse="") )
        }
        #pooled_stats <-read.table(file=cond_fileh, nrows = 2.5E6, colClasses = "numeric")
        pooled_stats <- scan(file=cond_fileh)
        print (str(pooled_stats_list))
        if ( is.data.frame(pooled_stats_list) ) {
          pooled_stats <- as.vector(pooled_stats[,1])
        }
        pooled_stats_list <-c(pooled_stats_list,list(pooled_stats))
      }
      print(str(pool_stats_all[side,region]))
      print(str(pooled_stats_list))
      #pool_stats_all[side,region] <- c(pool_stats_all[side,region],pooled_stats_list)
      pool_stats_all[side,region] <- pooled_stats_list

      #run the stat tests for the 7 pair comparisons. We may want to limi
      pooled_test_results<-list()
      for ( i in 1:7 ) {
        pooled_test_results <- c(pooled_test_results,list=list())
      }
      empty.df <- data.frame( two.sided=rep(0,7),less= rep(0,7),greater=rep(0,7) )
      p_values<-list(mwu.test=empty.df, ks.test = empty.df, welch.t.test=empty.df)

      for ( i in 1:7 ) {
        cond_1 = comparisons[i,1]
        cond_2 = comparisons[i,2]
        pooled_test_results[[i]] <-list(two.sided=c(),less=c(),greater=c())
        for (test.type in  hypothesis_ordinality) {

        kolmog.test.result<- ks.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],
                                           alternative=test.type,exact = NULL)
        p_values$ks.test[i,][test.type] <-kolmog.test.result$p.value

        wilcox.test.result <- wilcox.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],
                                               alternative=test.type,exact = FALSE,
                                               correct = FALSE)
        p_values$mwu.test[i,][test.type] <-wilcox.test.result$p.value
        welch.t.test.result <- t.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],    
                                           alternative = test.type,mu = 0, paired = FALSE, 
                                           var.equal = FALSE, conf.level = 0.95)

        p_values$welch.t.test[i,][test.type] <-welch.t.test.result$p.value
       pooled_test_results[[i]][test.type] <-list(ks.test=kolmog.test.result,wilcox.test = wilcox.test.result,t.test= welch.t.test.result)
      }

    }
    pool_stat_tests_all_regions_sides[side,region] <- c(pool_stat_tests_all_regions_sides[side,region],pooled_test_results)
  }
}
